### 2021-05-31 cued/experiments.tex
Modifications

However, from Figure~\ref{fig:polbooks-accuracy} we see that block 1 has low accuracy. This suggests that detected block 1 is not solely composed of ``neutral" books but also contains some ``liberal" and ``conservative" authors. Indeed, by examining Figure~\ref{fig:polbooks-graph} we see that block 1 is effectively a buffer between blocks 2 and 3 -- there are very few edges between blocks 2 and 3. It is therefore not surprising that some books from either side leak into block 1. Perhaps, the three distinct categories (``conservative", ``liberal", ``neutral") are too coarse a measure of political affiliation; it may be the case that the nominally ``conservative" books found in block 1 are in fact more centre-right. In the absence of more granular labels we cannot test this hypothesis. Nevertheless, political affiliation encoded as 3 distinct labels remains a fantastic predictor of network structure.

@@

The vast majority of blocks are composed of a single class. 
However, some blocks have two comparably good classes as their predictor. 
For example, both blocks 2 and 5 contain classes 3A and 3B as their 2 best predictors. 
This suggests that the social divide between classes is less pronounced 
for pupils in year 3. Conversely, some classes are found to extend over two 
detected blocks (class 2B spans blocks 8 and 9) but we do 
not have a feature which explains the division. The most surprising block 
is number 7, which has comparable weightings for classes 5A and 1B. 
Perhaps there was a joint event between those two classes on the day 
the data were collected. Nevertheless, a hierarchical approach would help further subdivide these blocks.

Figure~\ref{fig:school-accuracy} shows excellent accuracy for the majority of blocks. In fact the only blocks with low accuracy are those that have a school-class span two blocks such that we cannot reliably distinguish between the two. This is much more pronounced when we apply hard classification rather than the soft cross-entropy loss. Indeed block 1 has low accuracy because the class 1A has a higher weight component for block 3 than it does for block 1. As we use hard classification to compute accuracy, this means vertices belonging to class 1A are assigned to block 3. A similar effect is seen in block 5 which often loses out to block 2. Depending on the sample index $t$, class 2B is assigned to block 8 or 9 with maximal probability. This explains the rough 50\% accuracy for blocks 8 and 9.

@@

We choose $B=10$ and $D'=10$ for this experiment. The selected features 
(Figure~\ref{fig:fb-null}) are those that best explain the high-level 
community structure. The majority of them are education related. 
Nevertheless, for $D'=10$ we only have good explanations for the makeup 
of some of the detected blocks; several blocks in 
Figure~\ref{fig:fb-null} do not have high-magnitude components for $D'=10$. This is further emphasised by the disparate accuracies in Figure~\ref{fig:fb-accuracy}. Nevertheless, observe that the accuracy is only high for blocks that contain high magnitude weights. The only exception to this rule is block 9 which nonetheless, although this may have high magnitude weights just below the cut-off $c^*$. Recall that the accuracy is computed as ana average over all samples and so is likely to be lower than the MAP solution.
%
\begin{figure}[!h]
	\centering
	\begin{subfigure}[t]{0.45\linewidth}
		\centering
		\imagebox{7cm}{\includegraphics[width=\linewidth]{fb-null-1}}
		\caption{$\theta$-samples. Dotted line is $\pm c^*$.}
		\label{fig:fb-null}
	\end{subfigure}
	\begin{subfigure}[t]{0.45\linewidth}
		\centering
		\imagebox{7cm}{\includegraphics[width=\linewidth]{fb-accuracy-1}}
		\caption{Per-block accuracy $\eta(j)$.}
		\label{fig:fb-accuracy}
	\end{subfigure}
	\caption{Facebook egonet dataset.}
	\label{fig:fb}
\end{figure}

When the feature dimension is very large, it becomes increasingly likely that 
a particular feature may uniquely identify a small set of nodes. If these nodes 
are all part of the same community, then the classifier will overfit for that 
particular parameter. The regularisation term imposed by the prior goes some 
way towards alleviating this problem. Nevertheless, we see in 
Figure~\ref{fig:fb-null} that the feature \verb*|birthday-5| has a very 
high weight as it relates to block 1 -- but it is highly unlikely
that birthdays determine graphical structure.

However, we see the advantage of having $\Xcal=\{0,1\}$ rather than $\Xcal={-1, 1}$ as argued in Appendix \ref{appdx:dimension}. Block 1 in Figure~\ref{fig:fb-null} is allowed to contain 3 distinct feature categories. Nevertheless, one would have to apply a hierarchical approach to subdivide block 1 into smaller blocks to test whether these features determine structure at the lower-level.

>>>>

However, from Figure~\ref{fig:polbooks-accuracy} we see that block 1 has low accuracy. This suggests that detected block 1 is not solely composed of ``neutral" books but also contains some ``liberal" and ``conservative" authors. Indeed, by examining Figure~\ref{fig:polbooks-graph} we see that block 1 is effectively a buffer between blocks 2 and 3 -- there are very few edges between blocks 2 and 3. It is therefore not surprising that some books from either side leak into block 1. Perhaps, the three distinct categories (``conservative", ``liberal", ``neutral") are too coarse a measure of political affiliation; it may be the case that the nominally ``conservative" books found in block 1 are in fact more centre-right. In the absence of more granular labels, we cannot test this hypothesis. Nevertheless, political affiliation encoded as 3 distinct labels remains a fantastic predictor of network structure.

@@

The vast majority of blocks are composed of a single class. 
However, some blocks have two comparably strong classes as their predictors. 
For example, blocks 2 and 5 both contain classes 3A and 3B as their 2 best predictors. 
This suggests that the social divide between classes is less pronounced 
for pupils in year 3. Conversely, some classes are found to extend over two 
detected blocks (class 2B spans blocks 8 and 9) but we do 
not have a feature which explains the division. The most surprising block 
is number 7, which has comparable weightings for classes 5A and 1B. 
Perhaps there was a joint event between those two classes on the day 
the data were collected.

Figure~\ref{fig:school-accuracy} shows excellent accuracy for the majority of blocks. In fact the only blocks with low accuracy are those that have a school-class span two blocks such that we cannot reliably distinguish between the two. This is much more pronounced when we apply hard classification rather than the soft cross-entropy loss. Indeed block 1 has low accuracy because class 1A has a higher weight component for block 3 than it does for block 1. As we use hard classification to compute accuracy, vertices belonging to class 1A are predicted to belong to block 3. A similar effect is seen in block 5 which often loses out to block 2. The same can be said of blocks 8 and 9. However, in this case the weights for class 2B are very similar -- thus explaining the roughly evenly split accuracy for blocks 8 and 9.

@@

We choose $B=10$ and $D'=10$ for this experiment. The selected features 
(Figure~\ref{fig:fb-null}) are those that best explain the high-level 
community structure. The majority of them are education related. 
Nevertheless, for $D'=10$ we only have good explanations for the makeup 
of some of the detected blocks; several blocks in 
Figure~\ref{fig:fb-null} do not have high-magnitude components for $D'=10$. This is further emphasised by the disparate accuracies in Figure~\ref{fig:fb-accuracy}. Nevertheless, observe that the accuracy is only high for blocks that contain high magnitude weights. The only exception to this rule is block 9 which nonetheless may have high magnitude weights just below the cut-off $c^*$.
%
\begin{figure}[!h]
	\centering
	\begin{subfigure}[t]{0.45\linewidth}
		\centering
		\imagebox{7cm}{\includegraphics[width=\linewidth]{fb-null-1}}
		\caption{$\theta$-samples. Dotted line is $\pm c^*$.}
		\label{fig:fb-null}
	\end{subfigure}
	\begin{subfigure}[t]{0.45\linewidth}
		\centering
		\imagebox{7cm}{\includegraphics[width=\linewidth]{fb-accuracy-1}}
		\caption{Per-block accuracy $\eta(j)$.}
		\label{fig:fb-accuracy}
	\end{subfigure}
	\caption{Facebook egonet dataset.}
	\label{fig:fb}
\end{figure}

When the feature dimension is very large, it becomes increasingly likely that 
a particular feature may uniquely identify a small set of nodes. If these nodes 
are all part of the same community, then the classifier may overfit for that 
particular parameter. The regularisation term imposed by the prior goes some 
way towards alleviating this problem. Nevertheless, we see in 
Figure~\ref{fig:fb-null} that the feature \verb*|birthday-5| has a very 
high weight as it relates to block 1 -- but it is highly unlikely
that birthdays determine graphical structure. This issue could have been alleviated by choosing $\Xcal=\{-1, +1\}$ such that having a feature turned off supports excluding a vertex from the block. However, Figure~\ref{fig:fb-null} demonstrates why we made the deliberate choice $\Xcal=\{0,1\}$, as argued in Appendix \ref{appdx:dimension}. Because of the choice $\Xcal=\{0,1\}$, block 1 is allowed to contain 3 distinct feature categories rather than just one. We accept this tradeoff: risking spurious high magnitude components (e.g. \verb*|birthday-5|) for the benefit of allowing a top-level block span multiple feature-groups. Nevertheless, one would have to apply a hierarchical approach to subdivide each top-level block into sub-blocks to test whether the constituent feature-groups determine structure at the lower-level.

### 2021-05-31 cued/tech-abstract.tex
Modifications

We apply the proposed methods to a variety of network data
to extract the most important features along which the vertices
are partitioned. The main advantages of the proposed approach are
that the whole feature-space is used automatically and that features
can be rank-ordered implicitly according to impact. Any features
that do not significantly impact the high-level structure can be
discarded to reduce the problem dimension. In cases where the vertex
features available do not readily explain the community structure
in the resulting network, the approach detects this and is protected
against over-fitting. Results on several real-world datasets
illustrate the performance of the proposed methods.

>>>>

We apply the proposed methods to a variety of network data
to extract the most important features along which the vertices
are partitioned. The main advantages of the proposed approach are
that the whole feature-space is used automatically and that features
can be rank-ordered implicitly according to impact. Any features
that do not significantly impact the high-level structure can be
discarded to reduce the problem dimension. In cases where the vertex
features available do not readily explain the community structure
in the resulting network, the approach detects this and is protected
against over-fitting.

Future work on this topic could benefit from extending the FFBM to be hierarchical in nature. Such a modification would be relatively natural and would increase the descriptive power of the model. The current FFBM formulation is limited in that it can only explain structure at the macro-scale. Nevertheless, a hierarchical formulation would allow explanations of structure at any arbitrary length-scale.
